---
title: "Initial Korean covid 19"
author: "Kenroy Fuller"
date: "7/04/23"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
  
  
# Your Question - Is dying independent of sex?


## METHODS
We will examined the sex of the individual and verify the status if they are alive or dead. Also, we will used the helper file cat~cat to answers questions in this WUP_07 (title: "Initial Korean covid 19". 


## Graphical results - use ggplot commands to do this  

#### Plot barplots ggplot way

```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
The plot barplot chart show their more male of 70% dead than female is 50%. Their are 55% of female alive and 45% male. The reveal that men have an higher rate in dying than women.  
  

## Numerical results


```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
The table reveal that female have higher percentage in being alive than dead whareas the men higher percentage in dead than alive. The result for female alive is 98.7% and for male is 97%. The dead percentage for female is 1.4 % and male is 3%.


## Inferential results 




## Conclusions

